Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-02-13 joss/paper.rmd
Increases figure resolution

```{R load-script, echo = FALSE, results = "hide"}
library(CodeDepends)
library(Rclean)
```

```{R prov-graph, fig.cap = "Network diagram of the prospective data provenance generated for an example script. Arrows indicate which lines of code (numbered) produced which objects (named).", echo = FALSE}

>>>>

a```{R load-script, echo = FALSE, results = "hide"}
library(CodeDepends)
library(Rclean)
```

```{R prov-graph, dpi = 300, fig.cap = "Network diagram of the prospective data provenance generated for an example script. Arrows indicate which lines of code (numbered) produced which objects (named).", echo = FALSE}
